### 2020-03-04 s1_text/s1_text.tex
Update author list & acknowledgements

\begin{flushleft}
	{\Large
		\textbf\newline{Supporting information for ``theoretical investigation of a genetic switch for metabolic adaptation''}
	}
	\newline
	% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
		\\
	Kathrin S. Laxhuber\textsuperscript{1},
	Muir J. Morrison\textsuperscript{2},
	Rob Phillips\textsuperscript{2,3$\ast$}
	\\
	\bigskip
	\textbf{1} Department of Chemistry and Applied Biosciences, ETH Zurich, 8093 Zurich, Switzerland
	\\
	\textbf{2} Department of Physics, California Institute of Technology, Pasadena, CA, USA
	\\
	\textbf{3} Department of Biology and Biological Engineering, California Institute of Technology, Pasadena, CA, USA
	\\
	\bigskip

@@

\section{Experimental materials and methods} \label{sec:exp}

\textcolor{red}{missing}

@@

>>>>

\begin{flushleft}
	{\Large
		\textbf\newline{Supporting information for ``theoretical investigation of a genetic switch for metabolic adaptation''}
	}
	\newline
	% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
		\\
	Kathrin S. Laxhuber\textsuperscript{1},
	Muir J. Morrison\textsuperscript{2},
	Griffin Chure\textsuperscript{3},
	Rob Phillips\textsuperscript{2,3$\ast$}
	\\
	\bigskip
	\textbf{1} Department of Chemistry and Applied Biosciences, ETH Zurich, 8093 Zurich, Switzerland
	\\
	\textbf{2} Department of Physics, California Institute of Technology, Pasadena, CA, USA
	\\
	\textbf{3} Department of Biology and Biological Engineering, California Institute of Technology, Pasadena, CA, USA
	\\
	\bigskip

@@

\section{Experimental materials and methods} \label{sec:exp}
\paragraph{Construction of $\Delta{xapABR}$ deletion strain.} Cells containing
plasmid pSIM6 were diluted 1:100 in 50 ml LB media and grown to an OD600
of $\approx 0.4$ at $30 ^\circ$C. The culture was immediately placed in
a water bath shaker at 43$^\circ$C for 15 minutes and then cooled in an
ice bath for 10 minutes. Cells were then spun down for 10 minutes
(4,000~$g$, 4$^\circ$C) and resuspended on ice in 50~ml of chilled
water. This was repeated three times before resuspending in 200~$\mu$L
of chilled water to generate competent cells. Homologous primer
extension sequences were obtained from Baba {\it et al.} \cite{Baba2006}
and used to generate linear DNA containing a kanamycin resistance
gene insert by PCR (amplified from plasmid pKD4), using primers that.
contained homology for the region on the chromosome to be deleted
\cite{Datsenko2000}. Electroporation was performed using 1~$\mu$L
purified PCR product (about 100~ng DNA), mixed with 50~$\mu$L cells.
Cells were resuspended in 750~$\mu$L SOC media and outgrowth was
performed on a shaker at 30$^\circ$C for 90-120 minutes. Cells were then
selected on an LB-agar plate containing kanamycin (30~$\mu$g/ml) and
grown overnight at 30$^\circ$C. The deletions were confirmed by both
colony PCR and sequencing. After confirmation, the deletion was
transferred to a clean strain through P1 transduction and selection on
kanamycin. Removal of kanamycin resistance was achieved by transforming
cells with plasmid pCP20 (expressing FLP recombinase, carbenicillin
resistance, on a temperature-sensitive replicon), with cells grown at
30$^\circ$C. Lastly, several colonies were then growth colony-purified
once non-selectively at 43$^\circ$C and then tested for loss of
antibiotic resistance for both kanamycin and carbenicillin.

\paragraph{Construction of $\Delta{xapAB}$ strain.}
Further experiments are underway in which precise control of the xapR copy number are needed and the preliminary data from these experiments are shown in the middle panel of Fig. 2A of the main text. This strain was constructed by creating a XapR-mCherry fusion protein expressed from a tetR regulated promoter. This fusion construct was integrated into the ycbN locus of the $\Delta{xapABR}$ strain making an effective $\Delta{xapAB}$ strain. A pZS3-PN25-TetR expression plasmid was also inserted into this genetic background which permits titratable control over the xapR-mCherry copy number. For the data presented in this work, expression was maximized using 10~ng/mL of the tetR inducer anhydro-tetracycline. Further information of a similar construct (LacI-mCherry) can be found in~\cite{Brewster2014} and~\cite{Chure2019}.

\paragraph{Primers for deletion strains}
Generation of $\Delta{xapABR}$:
actatttccggcaattcctgtctcctcacctactgtgtcaatgcagccaaCATATGAATATCCTCCTTAG; $xapABR<>P2$
(lower case is homology, upper case is pKD4 primer)

agatacaacaggtatcgctaatatagaggaaagtgtcagagttaaaagatgttttttcatGTGTAGGCTGGAGCTGCTTC; $xapABR<>P1$ (lower case is homology, upper case is pKD4 primer)

Primers for colony-PCR to confirm deletion of xapABR:
(upstream of xapR) cgggtcgttagctcagttggta
(downstream of XapA): ttcccagtcgaagaacccgtac

\textbf{Finish reformatting to table, add other primers?}

@@

	\bibitem{Baba2006} Baba T, Ara T, Hasegawa M,
	Takai Y, Okumura Y, Baba, M, et al.
	\newblock Construction of \textit{Escherichia coli} K-12 in-frame,
	single-gene knockout mutants: the Keio collection.
	\newblock Molecular Systems Biology, 2006;2(1), 2460.
	\newblock doi:{10.1038/msb4100050}

	\bibitem{Datsenko2000}
	Datsenko, KA, Wanner, BL.
	\newblock One-step inactivation of chromosomal genes
	in Escherichia coli K-12 using PCR products.
	\newblock PNAS, 2000;97(12), 6640–6645.
	\newblock doi:{10.1073/pnas.120163297}
